Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-02 outputs/paper/paper.Rmd
fixed post-strat graphs

```{r eval=FALSE}
cleaned_data <- labelled::to_factor(cleaned_data)

# Plot Race
perc_race <- cleaned_data %>% count(race_ethnicity) %>% mutate(perc = n/nrow(cleaned_data))
race <- perc_race %>% ggplot(aes(x = race_ethnicity, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Race/Ethnicity of Respondents in 2018 ACS data",
                                                                               x = "Race/Ethnicity", y = "Percentage", subtitle = "Figure X")
race

# Plot Gender
perc_gender <- cleaned_data %>% count(gender) %>% mutate(perc = n/nrow(cleaned_data))
gender <- perc_gender %>% ggplot(aes(x = gender, y = perc)) + geom_bar(stat = "identity") + 
  labs(title = "Gender of Respondents in 2018 ACS data", x = "Gender", y = "Percentage", subtitle = "Figure X")
gender

# Plot education
perc_education <- cleaned_data %>% count(education) %>% mutate(perc = n/nrow(cleaned_data))
perc_education$education <- perc_education$education %>% factor(levels = c("High School or less", "Post Secondary Degree"))
education <- perc_education %>% ggplot(aes(x = education, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Education of Respondents in 2018 ACS data",
                                                                               x = "Education", y = "Percentage", subtitle = "Figure X")
summary(cleaned_data$education)
education

@@

perc_state$state <- perc_state$state %>% factor(levels = sort(as.character.factor(perc_state$state))) 
state <- perc_state %>% ggplot(aes(x = state, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "State of Respondents in 2018 ACS data", x = "State", y = "Percentage", subtitle = "Figure X")

state

# Plot age_group
perc_age_group <- cleaned_data %>% count(age_group) %>% mutate(perc = n/nrow(cleaned_data))
#perc_age_group$age_group <- perc_age_group$age_group %>% factor(levels = sort(as.character.factor(perc_age_group$age_group))) 
age_group <- perc_age_group %>% ggplot(aes(x = age_group, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Age of Respondents in 2018 ACS data",
                                                                               x = "Age Group", y = "Percentage", subtitle = "Figure X")
age_group
```

>>>>

```{r create post-strat plots, eval=FALSE}
cleaned_data <- labelled::to_factor(cleaned_data)

# Plot Race
perc_race <- cleaned_data %>% count(race_ethnicity) %>% mutate(perc = n/nrow(cleaned_data))
race <- perc_race %>% ggplot(aes(x = race_ethnicity, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Race/Ethnicity of Respondents in 2018 ACS data", x = "Race/Ethnicity", y = "Percentage", subtitle = "Figure X")

# Plot Gender
perc_gender <- cleaned_data %>% count(gender) %>% mutate(perc = n/nrow(cleaned_data))
gender <- perc_gender %>% ggplot(aes(x = gender, y = perc)) + geom_bar(stat = "identity") + 
  labs(title = "Gender of Respondents in 2018 ACS data", x = "Gender", y = "Percentage", subtitle = "Figure X")

# Plot education
perc_education <- cleaned_data %>% count(education) %>% mutate(perc = n/nrow(cleaned_data))
perc_education$education <- perc_education$education %>% factor(levels = c("High School or less", "Post Secondary Degree"))
education <- perc_education %>% ggplot(aes(x = education, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Education of Respondents in 2018 ACS data",
                                                                               x = "Education", y = "Percentage", subtitle = "Figure X")

@@

state <- perc_state %>% ggplot(aes(x = state, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "State of Respondents in 2018 ACS data", x = "State", y = "Percentage", subtitle = "Figure X")

# Plot age_group
perc_age_group <- cleaned_data %>% count(age_group) %>% mutate(perc = n/nrow(cleaned_data))
age_group <- perc_age_group %>% ggplot(aes(x = age_group, y = perc)) + geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Age of Respondents in 2018 ACS data",
                                                                               x = "Age Group", y = "Percentage", subtitle = "Figure X")
age_group
```
